Classless Java: Tuning Java Interfaces

### 2015-12-06 paper/sections/Translation.tex
section 5.5 reviewd

\subsection{Guaratees}
Now we try to understand what is the meaning of saying that our approach is correct, and more in general, what it means to say that a language tuning is correct.\haoyuan{Actually only self coherence is supported?}
We identify three types of guarantees:
\begin{itemize}
\item \textit{Self coherence}: the generated code itself is well-typed; type errors are not present in code the user have not wrote.
In our case it means that either \mixin{} produces in controlled way an understandable error, or the class can be successfully annotate and the generated code is well typed.
We guarantee \textit{Self coherence}.

@@

\item \textit{Heir coherence}: Interfaces (and in general classes) inheriting from instrumented code are well typed if they was well typed without the instrumentation.
This would require to not add any (default or abstract) method to the annotated interfaces, including type refinement.
\mixin  does not guarantee \textit{Heir coherence}.
Indeed consider the following example:

@@

\noindent This code is correct before the translation, but \mixin would  generate in \Q@B@  a method ``\Q@B withX(int x);@''.
This would break \Q@C@. 
Similarly, an expression of the form \Q@new B(){.. A withX(int x){..}}@ would compile before translation, but would be ill typed after the translation.
\end{itemize}

\noindent Our automatic type refinement 
is a usefull and convenient feature, but is not transparent to the heirs of the annotated interface. They need to be aware of the annotation semantic  to be well typed.

\subsection{Results}
To formally characterize the behaviour of our annotation, and the two level of guarancees that we offer, we provide some notations and two theorems:
\begin{itemize}
\item We say that an interface table 
IT is OK if under such interface table, all interfaces are OK.
\item Since interface tables are just represented as sequences of interfaces we can write IT = $\II$ IT' to talk about a specific interface in a table.
\item We denote with $\C^{\II}$ the name of an interface.
\item An interface table contains a hair of $\C$ if there is any interface that extends it, or any \Q@new@ that instantiate it.
\end{itemize}

@@

Informally, this means that for a client program that typechecks before a translation is applied, if the annotated type has no subtypes, and no objects of that type are created, then type safety is guaranteed after the successful translation. Conversely, the second step of \mixin, namely what \Q:@ObjWeak: does in the formalization, is guaranteed to be type-safe for the three kinds of coherence. The formal theorems proofs are available in Appendix~\ref{subsec:lemma1},~\ref{subsec:lemma2} and~\ref{subsec:theorem}.\\

>>>>

\subsection{Guaratees}
To understand to what extents our approach is correct (and more in general, what it means to say that a language tuning is correct) we identify three types of guarantees:
\begin{itemize}
\item \textit{Self coherence}: the generated code itself is well-typed; type errors are not present in code the user have not wrote.
In our case it means that either \mixin{} produces (in a controlled way) an understandable error, or the class can be successfully annotated and the generated code is well typed.
We guarantee \textit{Self coherence}.

@@

\item \textit{Heir coherence}: Interfaces (and in general classes) inheriting from instrumented code are well typed if they was well typed without the instrumentation.
This would require to not add any (default or abstract) method to the annotated interfaces, including type refinement.
\mixin  does not guarantee \textit{Heir coherence}.
Indeed consider the following:

@@

\noindent This code is correct before the translation, but \mixin would  generate in \Q@B@  a method ``\Q@B withX(int x);@''.
This would break \Q@C@. \\*
Similarly, an expression of the form ``\Q@new B(){.. A withX(int x){..}}@'' would compile before translation, but would be ill typed after the translation.
\end{itemize}

\noindent This means that our automatic type refinement 
is a usefull and convenient feature, but is not transparent to the heirs of the annotated interface. They need to be aware of the annotation semantic  and provide the right type while refining methods.

\subsection{Results}
To formally characterize the behaviour of our annotation, and the two level of guarancees that we offer, we provide some notations and two theorems:
\begin{itemize}
\item We denote with $\C^{\II}$ the name of an interface.
\item An interface table 
IT is OK if under such interface table, all interfaces are OK.
\item Since interface tables are just represented as sequences of interfaces we write IT = $\II$ IT' to select a specific interface in a table.
\item IT contains a heir of $\C$ if there is an interface that extends it, or a \Q@new@ that instantiate it.
\end{itemize}

@@

Informally, this means that for a client program that typechecks before a translation is applied, if the annotated type has no subtypes, and no objects of that type are created, then type safety is guaranteed after the successful translation. Conversely, the second step of \mixin, namely what \Q:@ObjWeak: does in the formalization, is guaranteed to be type-safe for the three kinds of coherence. The formal theorems proofs are available in Appendix.%~\ref{subsec:lemma1},~\ref{subsec:lemma2} and~\ref{subsec:theorem}.\\
